Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-21 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Fix `days_included` argument in draft code

```{r echo = FALSE, fig.height = 4, fig.width = 6}
#library(data.table)
#alex_gauge <- read.csv("/Users/joshuaferreri/Documents/NWR_Alex_Rain.csv", header = TRUE)
#save(alex_gauge, file = "writing/DraftExposurePaper/alex_gauge.RData")
load("alex_gauge.Rdata")
alex_nldas <- county_rain(counties = unique(alex_gauge$fips),
                             start_year = 2010, end_year = 2010,
                             rain_limit = 0, dist_limit = 1500,
                             days_include = c(-2, -1, 0, 1))
alex_nldas <- alex_nldas %>%
        filter(storm_id == "Alex-2010")
alex_gauge$fips <- as.character(alex_gauge$fips)
compare_rain <- right_join(alex_nldas, alex_gauge, by = "fips")
#alex_nldas <- as.data.table(alex_nldas)
#alex_gauge <- as.data.table(alex_gauge)
#compare_rain <- left_join(alex_nldas, alex_gauge, by = "fips")
a <- ggplot(compare_rain, aes(x = tot_precip, y = rain_mm,
                              color = fips)) +
        geom_point() + 
        theme_bw()
a
```

>>>>

```{r echo = FALSE, fig.height = 4, fig.width = 6}
#library(data.table)
#alex_gauge <- read.csv("/Users/joshuaferreri/Documents/NWR_Alex_Rain.csv", header = TRUE)
#save(alex_gauge, file = "writing/DraftExposurePaper/alex_gauge.RData")
load("alex_gauge.Rdata")
alex_nldas <- county_rain(counties = unique(alex_gauge$fips),
                             start_year = 2010, end_year = 2010,
                             rain_limit = 0, dist_limit = 1500,
                             days_included = c(-2, -1, 0, 1))
alex_nldas <- alex_nldas %>%
        filter(storm_id == "Alex-2010")
alex_gauge$fips <- as.character(alex_gauge$fips)
compare_rain <- right_join(alex_nldas, alex_gauge, by = "fips")
#alex_nldas <- as.data.table(alex_nldas)
#alex_gauge <- as.data.table(alex_gauge)
#compare_rain <- left_join(alex_nldas, alex_gauge, by = "fips")
a <- ggplot(compare_rain, aes(x = tot_precip, y = rain_mm,
                              color = fips)) +
        geom_point() + 
        theme_bw()
a
```
